MCTS Based on Simple Regret

### 2012-04-24 paper/srcr/paper.tex

We begin with background definitions and related work. 
Some sampling schemes are introduced, and shown to have better than UCB
bounds for the simple regret on sets, the first contribution of this paper. 
The results are applied to sampling in trees by combining the proposed sampling schemes on the
first step of a rollout with UCT for the rest of the
rollout. An additional sampling scheme based on metareasoning 
principles is also suggested, another contribution
of this paper.
Finally, the performance of the
proposed sampling schemes is evaluated on sets of Bernoulli arms, in randomly
generated 2-level trees, and on the sailing domain, showing where the proposed schemes have improved
performance, the third contribution of this paper.

@@

The UCT algorithm, an extension of UCB
to Monte-Carlo Tree Search is described in \cite{Kocsis.uct}, and
shown to outperform many state of the art search algorithms in both
MDP and adversarial search \cite{Eyerich.ctp}.

@@

\begin{dfn}
The \textbf{simple regret} $\IE r$ of a sampling policy for the Multi-armed Bandit
Problem is the expected difference between the best true expected reward
$\mu_*$ and the true expected reward $\mu_j$ of the empirically best arm
$j =\arg \max_i\overline X_i$:
\begin{equation}
\IE r=\sum_{j=1}^K\Delta_j\Pr(j=\arg\max_i\overline X_i)
\label{eqn:simple-regret}
\end{equation}
where $\Delta_j=\mu_*-\mu_j$.
\end{dfn}

@@

As the above ultimate goal is extremely difficult
to achieve, we introduce
simple schemes more amenable to analysis, loosely based on the metareasoning
concept of value of information, and compare
them to UCB (on sets) and UCT (in trees).

@@

We first consider $\varepsilon$-greedy sampling as a straightforward
generalization of uniform sampling:
\begin{dfn} The \textbf{$\mathbf{\varepsilon}$-greedy} sampling scheme
pulls the empirically best arm with probability
$0<\varepsilon<1$ and any other
arm with probability $\frac {1-\varepsilon} {K-1}$. 
\end{dfn}
This sampling scheme exhibits an exponentially decreasing simple regret:
\begin{thm} For every $0<\eta<1$  and $\gamma>1$ there exists $N$ such that for
  any number of samples $n>N$ the simple regret of the  $\varepsilon$-greedy
sampling scheme is  bounded from above as
\begin{equation}
\IE r_{\varepsilon\mbox{-}greedy}\le 2\gamma \sum_{i=1}^K\Delta_i\exp\left(\frac {-2\Delta_j^2n\varepsilon}
  {\left(1+\sqrt{\frac {(K-1)\varepsilon}
        {1-\varepsilon}}\right)^2}\right)
\end{equation}
with probability at least $1-\eta$.
\end{thm}

@@

Bound the probability $P_i$ that a non-optimal arm $i$ is selected. Split the interval
 $[\mu_i, \mu_*]$ at $\mu_i+\delta_i$. By Chernoff-Hoeffding bound:
\begin{eqnarray}
P_i&\le&\Pr[\overline X_i>\mu_i+\delta_i]+\Pr[\overline X_*<\mu_*-(\Delta_i-\delta_i)]\nonumber\\
   &\le&\exp\left(-2\delta_i^2n_i\right)+\exp\left(-2(\Delta_i-\delta_i)^2n_*\right)
\end{eqnarray}
Observe that, in probability, $\overline X_i \rightarrow \mu_i$ as $n\rightarrow\infty$, 
therefore $n_*\rightarrow n\varepsilon$, $n_i\rightarrow\frac
{n(1-\varepsilon)} {K-1}$ as $n\rightarrow \infty$. Conclude that for
any $0<\eta<1$, $\gamma>1$ there exists $N$ such that for any $n>N$ and
all non-optimal arms $i$:
\begin{equation}
P_i \le \gamma \left(\exp\left(\frac {-2\delta_i^2n(1-\varepsilon)}{K-1}\right)
+\exp\left(-2(\Delta_i-\delta_i)^2n\varepsilon\right)\right)
\label{eqn:epsgreedy-probbound}
\end{equation}
Require
\begin{eqnarray}
\exp\left(-\frac {2\delta_i^2n(1-\varepsilon)}{K-1}\right)
&=&\exp\left(-2(\Delta_i-\delta_i)^2n\varepsilon\right)\nonumber\\
\frac {\delta_i} {\Delta_i-\delta_i}&=&\sqrt{\frac {(K-1)\varepsilon} {1-\varepsilon}}
\label{eqn:epsgreedy-constant-varepsilon}
\end{eqnarray}
Substitute (\ref{eqn:epsgreedy-probbound}) together with
(\ref{eqn:epsgreedy-constant-varepsilon}) into
(\ref{eqn:simple-regret}) and obtain
\begin{equation}
\IE r_{\varepsilon\mbox{-}greedy}\le 2\gamma \sum_{i=1}^K\Delta_i\exp\left(\frac {-2\Delta_i^2n\varepsilon}
  {\left(1+\sqrt{\frac {(K-1)\varepsilon}
        {1-\varepsilon}}\right)^2}\right)
\end{equation}
\end{proof}

@@

$\varepsilon$-greedy is based solely on sampling the empirically best
arm with a higher probability then the rest of the arms, and ignores
information about empirical means of other arms. On the other hand,
UCB distributes samples in accordance with empirical means, but, in order to
minimize cumulative regret, chooses the empirically best arm too often.
Intuitively, a better scheme for simple regret minimization would
distribute samples in a way similar to UCB, but would sample the best arm
less. This can be achieved by replacing $\log(\cdot)$ in
Equation~\ref{eqn:ucb} with a faster growing sublinear function, for
example, $\sqrt\cdot$.
\begin{dfn} Scheme $\mathbf{UCB_{\sqrt{\cdot}}(c)}$ pulls arm $i$ that
maximizes $b_i$, where:
\begin{equation}
b_i=\overline X_i+\sqrt {\frac {c \sqrt n} {n_i}}
\end{equation}
where, as before, $\overline X_i$ is the average reward obtained from arm $i$,
$n_i$ is the number of times arm $i$ was pulled, and $n$ is the total
number of pulls so far. \end{dfn}
This scheme also exhibits a super-polynomially decreasing simple regret:
\begin{thm}  For every $0<\eta<1$  and $\gamma>1$ there exists $N$ such that for
  any number of samples $n>N$ the simple regret of the  UCB$_{\sqrt{\cdot}}$($c$)
sampling scheme is  bounded from above as
\begin{equation}
\IE r_{ucb\sqrt{\cdot}} \le
2\gamma\sum_{i=1}^K\Delta_i\exp\left(-\frac {c\sqrt{n}} 2\right)
\end{equation}
with probability at least $1-\eta$.
\end{thm}

\begin{proof}[Proof outline:] Bound the probability $P_i$ that a
  non-optimal arm $i$ is chosen. Split the interval $[\mu_i, \mu_*]$
  at $\mu_i+\frac {\Delta_i} 2$. By Chernoff-Hoeffding bound:
\begin{eqnarray}
P_i&\le&Pr\left[\overline X_i>\mu_i+\frac {\Delta_i} 2\right]+\Pr\left[\overline X_*<\mu_*-\frac {\Delta_i}
  2\right]\nonumber \\
   &\le&\exp\left(-\frac {\Delta_i^2n_i} 2\right)+\exp\left(-\frac {\Delta_i^2n_*} 2\right)
\end{eqnarray}
Observe that, in probability, $n_i\to \frac {c \sqrt n}
{\Delta_i^2}$, $n_i\le n_*$ as $n\to\infty$. Conclude that for
any $0<\eta<1$, $\gamma>1$ there exists $N$ such that for any $n>N$ and
all non-optimal arms $i$:
\begin{equation}
P_i \le 2\gamma \exp\left(-\frac {c \sqrt n} 2\right)
\label{eqn:usbsqrt-probbound}
\end{equation}
Substitute (\ref{eqn:usbsqrt-probbound}) into
(\ref{eqn:simple-regret}) and obtain
\begin{equation}
\IE r_{ucb\sqrt{\cdot}} \le 2\gamma\sum_{i=1}^K\Delta_i\exp\left(-\frac {c\sqrt{n}} 2\right)
\end{equation}
\end{proof}

@@

As mentioned above,
UCT \cite{Kocsis.uct} is an extension of UCB for MCTS, that
applies UCB($c$) at each step of a rollout.  At the root node,
the sampling in MCTS is usually aimed at finding the first move to perform. Search is re-started,
either from scratch or using some previously collected information,
after observing the actual outcome (in MDPs) or the opponent's move
(in adversarial games). Once one move is shown to be the best
choice with high confidence, the value of information of additional
samples of the best move is low. Therefore, one should be able to do
better than UCT by optimizing {\em simple regret}, rather than {\em
  cumulative regret}, at the root node.

Nodes deeper in the search tree are a different matter.
In order to support an optimal move choice at the root, a precise {\em value} of the search
tree nodes is beneficial. For these internal nodes, optimizing simple regret is not the answer, and 
cumulative regret optimization seems more reasonable. Lacking a complete metareasoning for sampling,
which would indicate the optimal way to sample both root nodes and internal nodes,
our suggested improvement to UCT thus combines different sampling schemes on the first step and
during the rest of each rollout:
\begin{dfn}
The \textbf{SR+CR MCTS sampling scheme} selects an action at the
current root node according to a scheme suitable for minimizing 
the simple regret (\textbf{SR}), such as $\frac 1 2$-greedy or UCB$_{\sqrt{\cdot}}$, and
then selects actions according to UCB, minimizing the cumulative regret (\textbf{CR}).
\end{dfn}

@@

We expect such two-stage sampling schemes to
outperform UCT and be
significantly less sensitive to the tuning of the exploration factor
$c$ of UCB($c$). That is since the contradiction between the need for a larger
value of $c$ on the first step (simple regret) and a smaller
value for the rest of the rollout (cumulative regret)
\cite{Bubeck.pure} is resolved. In fact, a sampling scheme that uses
UCB($c$) at all steps but a larger value of $c$ for the first step
than for the rest of the steps, should outperform UCT.

@@

If the distribution of results generated by the rollouts were known, the
above features could be easily computed. However, this is not the case for
most MCTS applications. Therefore, we estimate bounds on the feature values from
the current set of samples, based on the myopic assumption that the algorithm will only
sample one of the actions, and use these bounds as the feature values, to get:
\begin{eqnarray}
VOI_\alpha&\approx&\frac {\overline X_\beta} {n_\alpha+1}
\exp\left(-2(\overline X_\alpha - \overline X_\beta)^2 n_\alpha\right)\\
VOI_i&\approx&\frac {1-\overline X_\alpha} {n_i+1}
\exp\left(-2(\overline X_\alpha - \overline X_i)^2 n_i\right),\; i\ne\alpha\nonumber\\
\mbox{where }&&\alpha=\arg\max_i \overline X_i,\quad
             \beta=\arg\max_{i,\,i\ne\alpha} \overline X_i\nonumber
\end{eqnarray}
with $VOI_{\alpha}$ being (approximate) value for sampling the current best action,
and $VOI_i$ is the (approximate) value for sampling some other action $i$.

@@

These VOI estimates are used in the ``VOI-aware'' sampling scheme as follows: sample the
action that has maximum estimated VOI. We judged these estimates to be too crude
to be used as ``stopping criteria'' that can be used to cut off sampling,
leaving this issue for future research.
Unfortunately, this scheme appears too complicated to be amenable to a formal
analysis. Early experiments with this approach demonstrate a significantly lower simple regret.

@@

\begin{figure}[h!]
  \begin{minipage}[c]{1.0\linewidth}
    \centering
    \includegraphics[scale=0.8]{onelevel-tree.pdf}\\
    a. search tree, the best arm shaded
    \vspace{1em}
  \end{minipage}
  \begin{minipage}[c]{1.0\linewidth}
    \centering
    \includegraphics[scale=0.45]{flat-trilevel-k=64-uqb=8.pdf}\\
    b. regret vs. number of samples
  \end{minipage}
  \caption{Simple regret in MAB}
  \label{fig:mab-simple-regret}
\end{figure}

@@

Simple regret vs. the number of samples are shown for trees with root degree 16
(Figure~\ref{fig:mcts-regret}.b) and 64
(Figure~\ref{fig:mcts-regret}.c). The exploration factor $c$ is set to
$2$, the default value for rewards in the range $[0, 1]$.
The algorithms exhibit a similar relative performance: either $\frac 1
2$-greedy+UCT or UCB$_{\sqrt{\cdot}}$+UCT
gives the lowest regret, UCB$_{\sqrt{\cdot}}$+UCT dominates UCT everywhere
except for small numbers of instances. The advantage of both $\frac 1
2$-greedy+UCT and UCB$_{\sqrt{\cdot}}$+UCT grows with the number of arms.

\begin{figure}[h!]
  \begin{minipage}[c]{1.0\linewidth}
    \centering
    \includegraphics[scale=0.7]{twolevel-tree.pdf}\\
    a. search tree, the path to the best arm shaded
    \vspace{1em}
  \end{minipage}
  \begin{minipage}[c]{1.0\linewidth}
    \centering
    \includegraphics[scale=0.45]{tree-identity-k=16-uqb=8.pdf}\\ 
    b. 16 arms
    \vspace{0.5em}
  \end{minipage}
  \begin{minipage}[c]{1.0\linewidth}
    \centering
    \includegraphics[scale=0.45]{tree-identity-k=64-uqb=8.pdf} \\
    c. 64 arms
  \end{minipage}
  \caption{MCTS in random trees}
  \label{fig:mcts-regret}
\end{figure}

@@

Figure~\ref{fig:sailing-lake-size} shows the cost vs. the exploration
factor for lakes of different sizes. The relative difference between
the sampling schemes becomes more prominent when the lake size
increases.
\begin{figure}[h!]
   \centering
   \includegraphics[scale=0.45]{costs-size=6-nsamples=397.pdf}\\
   a. $6\times 6$ lake \\
   \vspace{1em}
   \includegraphics[scale=0.45]{costs-size=10-nsamples=397.pdf}\\
   b. $10\times 10$ lake
  \caption{The sailing domain, 397 samples, cost vs. factor}
  \label{fig:sailing-lake-size}
\end{figure}

@@

\section{Summary and Future Work}
\label{sec:summary}

@@

The MCTS SR+CR scheme presented in the paper differs
from UCT mainly in the first step of the rollout, when the `simple' selection
regret is minimized instead of the cumulative regret. Both the
theoretical analysis and the empirical evaluation provide evidence for
better general performance of the proposed scheme.

MCTS and UCT are particularly successful in Computer
Go \cite{GellyWang.mogo,Braudis.pachi,Enzenberger.Fuego}
and the proposed scheme should be evaluated on this domain, a
non-trivial task as Go programs typically use ``non-pure''
versions of UCT, extended with domain-specific knowledge.

@@

>>>>

We begin with background definitions and related work. 
Some sampling schemes are introduced, and shown to have better
bounds for the simple regret on sets than UCB, the first contribution of this paper. 
The results are applied to sampling in trees by combining the proposed sampling schemes on the
first step of a rollout with UCT for the rest of the
rollout. An additional sampling scheme based on metareasoning 
principles is also suggested, another contribution
of this paper.
Finally, the performance of the
proposed sampling schemes is evaluated on sets of Bernoulli arms, in randomly
generated 2-level trees, and on the sailing domain, showing where the proposed schemes have improved
performance.

@@

The UCT algorithm, an extension of UCB
to Monte-Carlo Tree Search is described in \cite{Kocsis.uct}, and
shown to outperform many state of the art search algorithms in both
MDP and adversarial games \cite{Eyerich.ctp,GellyWang.mogo}.

@@

\begin{dfn}
The \textbf{simple regret} $\IE r$ of a sampling policy for the Multi-armed Bandit
Problem is the expected difference between the best true expected reward
$\mu_*$ and the true expected reward $\mu_j$ of the arm with the greatest sample mean,
$j =\arg \max_i\overline X_i$:
\begin{equation}
\IE r=\sum_{j=1}^K\Delta_j\Pr(j=\arg\max_i\overline X_i)
\label{eqn:simple-regret}
\end{equation}
where $\Delta_j=\mu_*-\mu_j$.
\end{dfn}

@@

As the above ultimate goal is extremely difficult
to achieve, we introduce in this paper
simple schemes more amenable to analysis, loosely based on the metareasoning
concept of value of information, and compare
them to UCB (on sets) and UCT (in trees).

@@

We first consider $\varepsilon$-greedy sampling as a straightforward
generalization of uniform sampling:
\begin{dfn} The \textbf{$\mathbf{\varepsilon}$-greedy} sampling scheme
pulls the arm that currently has the greatst sample mean, with probability
$0<\varepsilon<1$, and any other
arm with probability $\frac {1-\varepsilon} {K-1}$. 
\end{dfn}
This sampling scheme exhibits an exponentially decreasing simple regret:
\begin{thm} For every $0<\eta<1$  and $\gamma>1$ there exists $N$ such that for
  any number of samples $n>N$ the simple regret of the  $\varepsilon$-greedy
sampling scheme is  bounded from above as
\begin{equation}
\IE r_{\varepsilon\mbox{-}greedy}\le 2\gamma \sum_{i=1}^K\Delta_i\exp\left(\frac {-2\Delta_j^2n\varepsilon}
  {\left(1+\sqrt{\frac {(K-1)\varepsilon}
        {1-\varepsilon}}\right)^2}\right)
\end{equation}
with probability at least $1-\eta$.
\end{thm}

@@

Bound the probability $P_i$ that a non-optimal arm $i$ is selected. Split the interval
 $[\mu_i, \mu_*]$ at $\mu_i+\delta_i$. Apply the Chernoff-Hoeffding bound to get:
\begin{eqnarray}
P_i&\le&\Pr[\overline X_i>\mu_i+\delta_i]+\Pr[\overline X_*<\mu_*-(\Delta_i-\delta_i)]\nonumber\\
   &\le&\exp\left(-2\delta_i^2n_i\right)+\exp\left(-2(\Delta_i-\delta_i)^2n_*\right)
\end{eqnarray}
Observe that, in probability, $\overline X_i \rightarrow \mu_i$ as $n\rightarrow\infty$, 
therefore $n_*\rightarrow n\varepsilon$, $n_i\rightarrow\frac
{n(1-\varepsilon)} {K-1}$ as $n\rightarrow \infty$. Conclude that for
every $0<\eta<1$, $\gamma>1$ there exists $N$ such that for every $n>N$ and
all non-optimal arms $i$:
\begin{equation}
P_i \le \gamma \left(\exp\left(\frac {-2\delta_i^2n(1-\varepsilon)}{K-1}\right)
+\exp\left(-2(\Delta_i-\delta_i)^2n\varepsilon\right)\right)
\label{eqn:epsgreedy-probbound}
\end{equation}
Require
\begin{eqnarray}
\exp\left(-\frac {2\delta_i^2n(1-\varepsilon)}{K-1}\right)
&=&\exp\left(-2(\Delta_i-\delta_i)^2n\varepsilon\right)\nonumber\\
\frac {\delta_i} {\Delta_i-\delta_i}&=&\sqrt{\frac {(K-1)\varepsilon} {1-\varepsilon}}
\label{eqn:epsgreedy-constant-varepsilon}
\end{eqnarray}
Substitute (\ref{eqn:epsgreedy-probbound}) together with
(\ref{eqn:epsgreedy-constant-varepsilon}) into
(\ref{eqn:simple-regret}) and obtain
\begin{equation}
\IE r_{\varepsilon\mbox{-}greedy}\le 2\gamma \sum_{i=1}^K\Delta_i\exp\left(\frac {-2\Delta_i^2n\varepsilon}
  {\left(1+\sqrt{\frac {(K-1)\varepsilon}
        {1-\varepsilon}}\right)^2}\right)
\end{equation}
\end{proof}

@@

$\varepsilon$-greedy is based solely on sampling the
arm that has the greatest sample mean (henceforth called the ``current best'' arm)
with a higher probability then the rest of the arms, and ignores
information about sample means of other arms. On the other hand,
UCB distributes samples in accordance with sample means, but, in order to
minimize cumulative regret, chooses the current best arm too often.
Intuitively, a better scheme for simple regret minimization would
distribute samples in a way similar to UCB, but would sample the current best arm
less often. This can be achieved by replacing $\log(\cdot)$ in
Equation~\ref{eqn:ucb} with a faster growing sublinear function, for
example, $\sqrt\cdot$.
\begin{dfn} Scheme $\mathbf{UCB_{\sqrt{\cdot}}(c)}$ pulls arm $i$ that
maximizes $b_i$, where:
\begin{equation}
b_i=\overline X_i+\sqrt {\frac {c \sqrt n} {n_i}}
\end{equation}
where, as before, $\overline X_i$ is the average reward obtained from arm $i$,
$n_i$ is the number of times arm $i$ was pulled, and $n$ is the total
number of pulls so far. \end{dfn}
This scheme also exhibits a super-polynomially decreasing simple regret:
\begin{thm}  For every $0<\eta<1$  and $\gamma>1$ there exists $N$ such that for
  any number of samples $n>N$ the simple regret of the  UCB$_{\sqrt{\cdot}}$($c$)
sampling scheme is  bounded from above as
\begin{equation}
\IE r_{ucb\sqrt{\cdot}} \le
2\gamma\sum_{i=1}^K\Delta_i\exp\left(-\frac {c\sqrt{n}} 2\right)
\end{equation}
with probability at least $1-\eta$.
\end{thm}

\begin{proof}[Proof outline:] Bound the probability $P_i$ that a
  non-optimal arm $i$ is chosen. Split the interval $[\mu_i, \mu_*]$
  at $\mu_i+\frac {\Delta_i} 2$. Apply the Chernoff-Hoeffding bound to get:
\begin{eqnarray}
P_i&\le&Pr\left[\overline X_i>\mu_i+\frac {\Delta_i} 2\right]+\Pr\left[\overline X_*<\mu_*-\frac {\Delta_i}
  2\right]\nonumber \\
   &\le&\exp\left(-\frac {\Delta_i^2n_i} 2\right)+\exp\left(-\frac {\Delta_i^2n_*} 2\right)
\end{eqnarray}
Observe that, in probability, $n_i\to \frac {c \sqrt n}
{\Delta_i^2}$, $n_i\le n_*$ as $n\to\infty$. Conclude that for
every $0<\eta<1$, $\gamma>1$ there exists $N$ such that for every $n>N$ and
all non-optimal arms $i$:
\begin{equation}
P_i \le 2\gamma \exp\left(-\frac {c \sqrt n} 2\right)
\label{eqn:usbsqrt-probbound}
\end{equation}
Substitute (\ref{eqn:usbsqrt-probbound}) into
(\ref{eqn:simple-regret}) and obtain
\begin{equation}
\IE r_{ucb\sqrt{\cdot}} \le 2\gamma\sum_{i=1}^K\Delta_i\exp\left(-\frac {c\sqrt{n}} 2\right)
\end{equation}
\end{proof}

@@

As mentioned above,
UCT \cite{Kocsis.uct} is an extension of UCB for MCTS, that
applies UCB($c$) at each step of a rollout.  At the root node,
the sampling in MCTS is usually aimed at finding the first move to perform. Search is re-started,
either from scratch or using some previously collected information,
after observing the actual outcome (in MDPs) or the opponent's move
(in adversarial games). Once one move is shown to be the best
choice with high confidence, the value of information of additional
samples of the best move (or, in fact, of any other samples) is low. Therefore, one should be able to do
better than UCT by optimizing {\em simple regret}, rather than {\em cumulative regret}, at the root node.

Nodes deeper in the search tree are a different matter.
In order to support an optimal move choice at the root, it is beneficial in many cases
to find a more precise estimate of the {\em value} of the state in these search
tree nodes. For these internal nodes, optimizing simple regret is not the answer, and 
cumulative regret optimization is not so far off the mark. Lacking a complete metareasoning for sampling,
which would indicate the optimal way to sample both root nodes and internal nodes,
our suggested improvement to UCT thus combines different sampling schemes on the first step and
during the rest of each rollout:
\begin{dfn}
The \textbf{SR+CR MCTS sampling scheme} selects an action at the
current root node according to a scheme suitable for minimizing 
the simple regret (\textbf{SR}), such as $\frac 1 2$-greedy or UCB$_{\sqrt{\cdot}}$, and (at non-root nodes)
then selects actions according to UCB, which approximately minimizes the cumulative regret (\textbf{CR}).
\end{dfn}

@@

We expect such two-stage sampling schemes to
outperform UCT and be
significantly less sensitive to the tuning of the exploration factor
$c$ of UCB($c$). That is since the contradiction between the need for a larger
value of $c$ on the first step (simple regret) and a smaller
value for the rest of the rollout (cumulative regret)
\cite{Bubeck.pure} is resolved. In fact, a sampling scheme that uses
UCB($c$) at all steps but a larger value of $c$ for the first step
than for the rest of the steps, should also outperform UCT.

@@

If the distribution of results generated by the rollouts were known, the
above features could be easily computed. However, this is not the case for
most MCTS applications. Therefore, we estimate bounds on the feature values from
the current set of samples, based on the myopic assumption that the algorithm will only
sample one of the actions, and use these bounds as the feature values, to get:
\begin{eqnarray}
VOI_\alpha&\approx&\frac {\overline X_\beta} {n_\alpha+1}
\exp\left(-2(\overline X_\alpha - \overline X_\beta)^2 n_\alpha\right)\\
VOI_i&\approx&\frac {1-\overline X_\alpha} {n_i+1}
\exp\left(-2(\overline X_\alpha - \overline X_i)^2 n_i\right),\; i\ne\alpha\nonumber\\
\mbox{where }&&\alpha=\arg\max_i \overline X_i,\quad
             \beta=\arg\max_{i,\,i\ne\alpha} \overline X_i\nonumber
\end{eqnarray}
with $VOI_{\alpha}$ being the (approximate) value for sampling the current best action,
and $VOI_i$ is the (approximate) value for sampling some other action $i$.

@@

These VOI estimates are used in the ``VOI-aware'' sampling scheme as follows: sample the
action that has maximum estimated VOI. We judged these estimates to be too crude
to be used as ``stopping criteria'' that can be used to cut off sampling,
leaving this issue for future research.
Although this scheme appears too complicated to be amenable to a formal
analysis, early experiments (Section \ref{sec:emp})
with this approach demonstrate a significantly lower simple regret.

@@

\begin{figure}[h!]
  \begin{minipage}[c]{1.0\linewidth}
    \centering
    \includegraphics[scale=0.8]{onelevel-tree.pdf}\\
    a. search tree, with best arm shaded
    \vspace{1em}
  \end{minipage}
  \begin{minipage}[c]{1.0\linewidth}
    \centering
    \includegraphics[scale=0.45]{flat-trilevel-k=64-uqb=8.pdf}\\
    b. regret vs. number of samples
  \end{minipage}
  \caption{Simple regret in MAB}
  \label{fig:mab-simple-regret}
\end{figure}

@@

Simple regret vs. the number of samples are shown for trees with root degree 16
(Figure~\ref{fig:mcts-regret}.b) and 64
(Figure~\ref{fig:mcts-regret}.c). The exploration factor $c$ is set to
$2$, the default value for rewards in the range $[0, 1]$.
The algorithms exhibit a similar relative performance: either $\frac 1
2$-greedy+UCT or UCB$_{\sqrt{\cdot}}$+UCT
result in the lowest regret, UCB$_{\sqrt{\cdot}}$+UCT dominates UCT everywhere
except when the number of samples is small. The advantage of both $\frac 1
2$-greedy+UCT and UCB$_{\sqrt{\cdot}}$+UCT grows with the number of arms.

\begin{figure}[h!]
  \begin{minipage}[c]{1.0\linewidth}
    \centering
    \includegraphics[scale=0.7]{twolevel-tree.pdf}\\
    a. search tree, with path to the best arm shaded
    \vspace{1em}
  \end{minipage}
  \begin{minipage}[c]{1.0\linewidth}
    \centering
    \includegraphics[scale=0.45]{tree-identity-k=16-uqb=8.pdf}\\ 
    b. 16 arms
    \vspace{0.5em}
  \end{minipage}
  \begin{minipage}[c]{1.0\linewidth}
    \centering
    \includegraphics[scale=0.45]{tree-identity-k=64-uqb=8.pdf} \\
    c. 64 arms
  \end{minipage}
  \caption{MCTS in random trees}
  \label{fig:mcts-regret}
\end{figure}

@@

Figure~\ref{fig:sailing-lake-size} shows the cost vs. the exploration
factor for lakes of different sizes. The relative difference between
the sampling schemes becomes more prominent when the lake size
increases.
\begin{figure}[h!]
   \centering
   \includegraphics[scale=0.45]{costs-size=6-nsamples=397.pdf}\\
   a. $6\times 6$ lake \\
   \vspace{1em}
   \includegraphics[scale=0.45]{costs-size=10-nsamples=397.pdf}\\
   b. $10\times 10$ lake
  \caption{The sailing domain, 397 rollouts, cost vs. factor}
  \label{fig:sailing-lake-size}
\end{figure}

@@

\section{Conclusion and Future Work}
\label{sec:summary}

@@

The MCTS SR+CR scheme presented in the paper differs
from UCT mainly in the first step of the rollout, when we attempt to minimize
the `simple' selection regret rather than the cumulative regret. Both the
theoretical analysis and the empirical evaluation provide evidence for
better general performance of the proposed scheme.

@@

Finally, applying VOI methods in complex deployed applications that already use
MCTS is a challenge that should be addressed in future work.
In particular, UCT is extremely successful in Computer
Go \cite{GellyWang.mogo,Braudis.pachi,Enzenberger.Fuego},
and the proposed scheme should be evaluated on this domain. This is non-trivial, since
Go programs typically use ``non-pure'' versions of UCT, extended with
domain-specific knowledge. For example, Pachi \cite{Braudis.pachi}
typically re-uses information from rollouts generated for earlier
moves, thereby violating our underlying assumption that information is
only used for selecting the current move.  In early experiments not
shown here (disallowing re-use of samples, admittedly not really a
fair comparison) the VOI-aware scheme apears to dominate UCT.
Nevertheless, it should also be possible to adapt the VOI-aware
schemes to take into account expected re-use of samples, another topic
for future research.
